---
title: "Analysis"
author: "Caroline Simpson"
format: pdf
editor: visual
---

```{r}

library(rstatix)
library(tidyverse)
library(haven)
library(jtools)
library(forcats)

```

# Variables

```{r}


```

```{r}
draw_interaction_plot <- function(x, trace, y, x_label, trace_label, y_label) {

  
  df<- na.omit(data.frame(x, trace, y))
  
  interaction.plot(x.factor = df$x, 
                   trace.factor = df$trace, 
                   response = df$y, 
                   fun = mean, type = "b", 
                   xlab = x_label, 
                   ylab=y_label, 
                   trace.label = trace_label,
                   col="blue", pch=1:5)
}

simple_effects_between_anova <- function(data, tom_value, dv, between) {
  subset_data <- data |> filter(tom == tom_value)
  # model <- lm(as.formula(formula), data = subset_data)
  model <- anova_test(data = subset_data, dv = dv, between = between, detailed=TRUE)
  get_anova_table(model)
}

simple_effects_within_anova <- function(data, condition, dv, within) {
  subset_data <- subset(data, Condition == condition)
  model <- anova_test(data = subset_data, dv = dv, wid = ResponseId, within = within, detailed=TRUE)
  get_anova_table(model)
}


violin_plot <- function(data, x, y, group, title) {
  data |>
    ggplot(aes(x = x, y = y)) +
    geom_violin(alpha = 0.5, draw_quantiles = c(0.5)) +
    ggtitle(title) 
}

```

```{r}
raw_data <- read_spss(
  #"data/Thesis+-+Trusting+the+Machine+-+Copy+For+Testing_December+4,+2024_21.34.sav"
  # "data/Thesis+-+Trusting+the+Machine_December+4,+2024_19.13.sav"
  # "data/Thesis+-+Trusting+the+Machine_November+30,+2024_13.06.sav"
  "data/Thesis+-+Trusting+the+Machine_December+6,+2024_16.22.sav"
  )


raw_data$Appelman_1 <- as.numeric(as.character(raw_data$Appelman_1))
raw_data$Appelman_2 <- as.numeric(as.character(raw_data$Appelman_2))
raw_data$Appelman_3 <- as.numeric(as.character(raw_data$Appelman_3))
raw_data$Appelman_4 <- as.numeric(as.character(raw_data$Appelman_4))
raw_data$Appelman_5 <- as.numeric(as.character(raw_data$Appelman_5))
raw_data$Appelman_6 <- as.numeric(as.character(raw_data$Appelman_6))

raw_data$TrustBehaviour_1 <- as.numeric(as.character(raw_data$TrustBehaviour_1))
raw_data$TrustBehaviour_2 <- as.numeric(as.character(raw_data$TrustBehaviour_2))
raw_data$TrustBehaviour_3 <- as.numeric(as.character(raw_data$TrustBehaviour_3))
raw_data$TrustBehaviour_4 <- as.numeric(as.character(raw_data$TrustBehaviour_4))
raw_data$TrustBehaviour_5 <- as.numeric(as.character(raw_data$TrustBehaviour_5))
raw_data$TrustBehaviour_6 <- as.numeric(as.character(raw_data$TrustBehaviour_6))
raw_data$TrustBehaviour_7 <- as.numeric(as.character(raw_data$TrustBehaviour_7))
raw_data$TrustBehaviour_8 <- as.numeric(as.character(raw_data$TrustBehaviour_8))
raw_data$TrustBehaviour_9 <- as.numeric(as.character(raw_data$TrustBehaviour_9))
# raw_data <- read_csv("data/test_data.csv")
```

Number of participants = `r nrow(raw_data)`.

## Clean data

Filter out incomplete results

```{r}
cleaned_data <- raw_data |>
  filter(EndDate >= "2024-12-04") |>
  #filter(EndDate < "2024-12-04") |>
  filter(Progress == 100) |>
  filter(ConsentForm == 1) |>
  filter(Status == 0) # Anonymous link
  #filter(Status == 1) # Preview link
```

Number of participants = `r nrow(cleaned_data)`.

```{r}
cleaned_data |> filter(Reread == 1)
```

Filter out incorrect topic check

```{r}
cleaned_data <- cleaned_data |>
  filter(TopicCheck == 1)
```

Number of participants passing topic checks = `r nrow(cleaned_data)`.

```{r}
# print_labels(cleaned_data$AgentTypeCheck)
# print_labels(cleaned_data$AgentNameCheck)

```

```{r}
cleaned_data$Condition <- as.factor(cleaned_data$Condition)
print(cleaned_data$Condition)
```

Filter out incorrect agent check

```{r}
cleaned_data <- cleaned_data |>
  filter((AgentTypeCheck == 1 & Condition == "Low") | (AgentTypeCheck == 1 & Condition == "Medium") | (AgentTypeCheck == 2 & Condition == "High") )
```

```{r}

glimpse(select(cleaned_data, GodspeedMETI_28:GodspeedMETI_29, Condition))
```

Filter out incorrect attention check

```{r}
cleaned_data <- cleaned_data |>
  filter(GodspeedMETI_28 == 100) |>
  filter(GodspeedMETI_29 == 0)
```

Number of participants passing attention checks = `r nrow(cleaned_data)`.

```{r}
cleaned_data <- cleaned_data |>
  filter(Q_RecaptchaScore == 1)
```

Number of participants with recaptcha score of 1 = `r nrow(cleaned_data)`.

```{r}

cleaned_data <- cleaned_data |>
  filter(Unrealistic_2_TEXT != "A3HPLIWSXW3XV8")
```

Number of participants that didn't seem like bots on manual inspection = `r nrow(cleaned_data)`.

### Reverse code items

```{r}

# 4, 5

cleaned_data <- cleaned_data |> 
  mutate(
    TrustBehaviour_4r = 7 - TrustBehaviour_4,
    TrustBehaviour_5r = 7 - TrustBehaviour_5,
    GodspeedMETI_10r = 100 - GodspeedMETI_10,
    GodspeedMETI_13r = 100 - GodspeedMETI_13,
    GodspeedMETI_15r = 100 - GodspeedMETI_15,
    GodspeedMETI_16r = 100 - GodspeedMETI_16,
    GodspeedMETI_17r = 100 - GodspeedMETI_17,
    GodspeedMETI_18r = 100 - GodspeedMETI_18,
    GodspeedMETI_19r = 100 - GodspeedMETI_19,
    GodspeedMETI_20r = 100 - GodspeedMETI_20,
    GodspeedMETI_21r = 100 - GodspeedMETI_21,
    GodspeedMETI_22r = 100 - GodspeedMETI_22,
    GodspeedMETI_23r = 100 - GodspeedMETI_23,
    GodspeedMETI_24r = 100 - GodspeedMETI_24,
    GodspeedMETI_25r = 100 - GodspeedMETI_25,
    GodspeedMETI_26r = 100 - GodspeedMETI_26,
  )


```

## Calculate scores

TODO: reliability analysis on Godspeed items

```{r}

cleaned_data <- cleaned_data |>
  mutate(
    content_trust_score = rowMeans(select(cleaned_data, Appelman_1:Appelman_3), na.rm = TRUE),
    content_trust_score_2 = rowMeans(select(cleaned_data, c(TrustBehaviour_1, TrustBehaviour_2,  TrustBehaviour_3 ,TrustBehaviour_4r, TrustBehaviour_5r, TrustBehaviour_6, TrustBehaviour_9)), na.rm = TRUE),
    author_trust_score = rowMeans(select(cleaned_data, c(TrustBehaviour_7, TrustBehaviour_8)), na.rm = TRUE),
    anthropomorphism_score = rowMeans(select(cleaned_data, GodspeedMETI_1:GodspeedMETI_4), na.rm = TRUE),
    likeability_score = rowMeans(select(cleaned_data, GodspeedMETI_5:GodspeedMETI_9), na.rm = TRUE),
    competence_score = rowMeans(select(cleaned_data, GodspeedMETI_10:GodspeedMETI_14), na.rm = TRUE), 
    expertise_score = rowSums(select(cleaned_data, c(GodspeedMETI_10, GodspeedMETI_13, GodspeedMETI_15r:GodspeedMETI_18r)), na.rm = TRUE), 
    integrity_score = rowSums(select(cleaned_data, GodspeedMETI_19r:GodspeedMETI_22r), na.rm = TRUE), 
    benevolence_score = rowSums(select(cleaned_data, GodspeedMETI_23r:GodspeedMETI_26r), na.rm = TRUE),
    METI_author_trust_score = rowSums(select(cleaned_data, c(GodspeedMETI_10, GodspeedMETI_13, GodspeedMETI_15r:GodspeedMETI_18r, GodspeedMETI_19r:GodspeedMETI_22r, GodspeedMETI_23r:GodspeedMETI_26r)), na.rm = TRUE)
  ) 



```

# Descriptive Statistics

```{r}

cleaned_data |>
  select(Condition, anthropomorphism_score) |>
by(cleaned_data$Condition, summary)


```

Standard Deviation

```{r}

tapply(cleaned_data$anthropomorphism_score, cleaned_data$Condition, sd)

```

Variance

```{r}
tapply(cleaned_data$anthropomorphism_score, cleaned_data$Condition, var)
```

```{r}
library(pastecs)

cleaned_data |>
  select(Condition, ends_with("_score") ) |>
by(cleaned_data$Condition, stat.desc)
```

# Plots of score distributions

```{r}

violin_plot(cleaned_data, cleaned_data$Condition, cleaned_data$anthropomorphism_score, cleaned_data$Condition, "Anthropomorphism Scores")

violin_plot(cleaned_data, cleaned_data$Condition, cleaned_data$likeability_score, cleaned_data$Condition, "Likeability Scores")

violin_plot(cleaned_data, cleaned_data$Condition, cleaned_data$competence_score, cleaned_data$Condition, "Competence Scores")

violin_plot(cleaned_data, cleaned_data$Condition, cleaned_data$content_trust_score, cleaned_data$Condition, "Content Trust Scores")

violin_plot(cleaned_data, cleaned_data$Condition, cleaned_data$content_trust_score_2,
            cleaned_data$Condition, "Content Trust Scores - Custom Scale")

violin_plot(cleaned_data, cleaned_data$Condition, cleaned_data$author_trust_score, cleaned_data$Condition, "Author Trust Scores - Custom Scale")

violin_plot(cleaned_data, cleaned_data$Condition, cleaned_data$METI_author_trust_score, cleaned_data$Condition, "Author Trust Scores - METI")

violin_plot(cleaned_data, cleaned_data$Condition, cleaned_data$expertise_score, cleaned_data$Condition, "Expertise Scores")

violin_plot(cleaned_data, cleaned_data$Condition, cleaned_data$integrity_score, cleaned_data$Condition, "Integrity Scores")

violin_plot(cleaned_data, cleaned_data$Condition, cleaned_data$benevolence_score, cleaned_data$Condition, "Benevolence Scores")
```

```{r}
# ANOVA_anthropomorphism_score <- anova_test(data = cleaned_data, dv = anthropomorphism_score, between = Condition, detailed=TRUE)
# get_anova_table(ANOVA_anthropomorphism_score)


```

```{r}
library(performance)
library(see)

lm_anthropomorphism_score <- lm(anthropomorphism_score ~ Condition, data = cleaned_data)
summ(lm_anthropomorphism_score)

check_model(lm_anthropomorphism_score, panel = FALSE)
```

```{r}

lm_content_trust_score <- lm(content_trust_score ~ Condition * Gender, data = cleaned_data)
summ(lm_content_trust_score)

draw_interaction_plot(cleaned_data$Gender, cleaned_data$Condition, cleaned_data$content_trust_score, "Gender", "Condition", "Content Trust")

check_model(lm_content_trust_score, panel = FALSE)


```

```{r}
longer_data <- cleaned_data |>
  # filter(GodspeedMETI_1 != 0 | GodspeedMETI_2 != 0 | GodspeedMETI_3 != 0 | GodspeedMETI_4 != 0) |>
  pivot_longer(GodspeedMETI_1:GodspeedMETI_14, names_to = "item", values_to = "rating")

longer_data$Condition <- as.factor(longer_data$Condition)
longer_data$item <- as.factor(longer_data$item)

longer_data |>
    ggplot(aes(x = item, y = rating, colour = Condition)) +
    geom_jitter() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  
```

```{r}
high_plot <- longer_data |>
  filter(Condition == "High") |>
  ggplot(aes(x = item, y = rating, colour = ResponseId)) +
    geom_jitter() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
high_plot

ggsave("high.jpg", high_plot, width = 40, height = 20, units = "cm")

```

```{r}
medium_plot <- longer_data |>
  filter(Condition == "Medium") |>
  ggplot(aes(x = item, y = rating, colour = ResponseId)) +
    geom_jitter() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


medium_plot

ggsave("medium.jpg", medium_plot, width = 40, height = 20, units = "cm")

```

```{r}
low_plot <- longer_data |>
  filter(Condition == "Low") |>
  ggplot(aes(x = item, y = rating, colour = ResponseId)) +
    geom_jitter() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

low_plot
  ggsave("low.jpg", low_plot, width = 40, height = 20, units = "cm")
```

```{r}
# cleaned_data |>
#   select(GodspeedMETI_1:GodspeedMETI_29, Condition) |>
#   filter(if_any(starts_with("Godspeed"), ~ . < 5)) |>
#   glimpse()
```

```{r}

# cleaned_data$GodspeedMETI_1 %>% attr('label')
# 
# for (i in colnames(cleaned_data)){
#     print(paste(i, attr(cleaned_data[[i]], 'label')))
# }
```

```{r}

```

```{r}
# cleaned_data |>
#   select(Condition, anthropomorphism_score, ResponseId) |>
#   pivot_wider(names_from = ResponseId, values_from = anthropomorphism_score)
# 

```

```{r}

# anthro <- cleaned_data |>
#   select(Condition, starts_with("GodspeedMETI"), ResponseId) |> 
#   arrange(Condition, GodspeedMETI_1, GodspeedMETI_2, GodspeedMETI_3, GodspeedMETI_4)
#   # select(Condition, GodspeedMETI_1, GodspeedMETI_2, GodspeedMETI_3, GodspeedMETI_4, ResponseId) |> 
#   # arrange(Condition, GodspeedMETI_1, GodspeedMETI_2, GodspeedMETI_3, GodspeedMETI_4)
# 
# glimpse(anthro)
```

```{r}

library(FactoMineR)
library(factoextra) 

anthro_cluster_df <- cleaned_data|> 
  select(Gender, Education, AIChatbotsFrequency, ScienceContent, Age_1, Experience_1:Experience_11)
  # select(anthropomorphism_score, likeability_score, author_trust_score, content_trust_score, content_trust_score_2, METI_author_trust_score, expertise_score)

anthro.pca <- PCA(anthro_cluster_df,  graph = FALSE)
get_eig(anthro.pca)


```

```{r}

fviz_screeplot(anthro.pca, addlabels = TRUE, ylim = c(0, 50))

```

```{r}
anthro.var <- get_pca_var(anthro.pca)

head(anthro.var$coord)

head(anthro.var$contrib)

fviz_pca_var(anthro.pca, col.var = "black")
```

```{r}
fviz_pca_var(anthro.pca, col.var="contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE # Avoid text overlapping
             )
```

```{r}

# Contributions of variables to PC1
fviz_contrib(anthro.pca, choice = "var", axes = 1, top = 10)

# Contributions of variables to PC2
fviz_contrib(anthro.pca, choice = "var", axes = 2, top = 10)
```

```{r}

ind <- get_pca_ind(anthro.pca)
ind

head(ind$coord)


fviz_pca_ind(anthro.pca, col.ind = "cos2",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE # Avoid text overlapping (slow if many points)
             )

```

```{r}

# Biplot of individuals and variables
fviz_pca_biplot(anthro.pca, repel = TRUE)
```

# K-Means Clustering

```{r}

library(cluster)

data_for_cluster <- cleaned_data|> 
  select(Unrealistic, Condition, Gender) |>
  # select(Gender, Education, AIChatbotsFrequency, ScienceContent, Age_1, Experience_1:Experience_11) |>
  mutate(Condition = case_when(Condition == "Low" ~ 1,
                               Condition == "Medium" ~ 2,
                               Condition == "High" ~3)) |>
  mutate(mutate(across(where(is.numeric), scale)))
  


set.seed(123)  # For reproducibility
fviz_nbclust(data_for_cluster, kmeans, method = "wss")
```

```{r}
set.seed(123)
kmeans_result <- kmeans(data_for_cluster, centers = 6)  # Replace 3 with optimal clusters
data_for_cluster$Cluster <- as.numeric(kmeans_result$cluster)
cleaned_data$Cluster.kmeans <- as.numeric(kmeans_result$cluster)

fviz_cluster(kmeans_result, data = data_for_cluster)

data_for_cluster <- data_for_cluster|>
  select(-Cluster)
```

```{r}
cleaned_data |>
    ggplot(aes(x = Cluster.kmeans, y = anthropomorphism_score, colour = Cluster.kmeans)) +
  geom_jitter() + 
    # geom_violin(alpha = 0.5, draw_quantiles = c(0.5)) +
    ggtitle("Anthropomorphism Scores (K-Means Clustering)") +
  facet_grid(vars(Condition))

```

# Hierarchical Clustering

```{r}


dist_matrix <- dist(data_for_cluster, method = "euclidean")

hclust_result <- hclust(dist_matrix, method = "ward.D2")

plot(hclust_result)
rect.hclust(hclust_result, k = 8, border = "red")  # Replace 3 with desired clusters

cleaned_data$Cluster.hierarchical <- cutree(hclust_result, k = 8)
```

```{r}

cleaned_data |>
    ggplot(aes(x = Cluster.hierarchical, y = anthropomorphism_score, colour = Cluster.hierarchical)) +
  geom_jitter() + 
    # geom_violin(alpha = 0.5, draw_quantiles = c(0.5)) +
    ggtitle("Anthropomorphism Scores (K-Means Clustering)") +
  facet_grid(vars(Condition))
```

```{r}

pam_result <- pam(data_for_cluster, k = 3)  # Replace 3 with the optimal number of clusters

fviz_cluster(pam_result, data = data_for_cluster)

cleaned_data$Cluster.pam<- as.numeric(pam_result$cluster)
```

```{r}

cleaned_data |>
    ggplot(aes(x = Cluster.pam, y = anthropomorphism_score, colour = Cluster.pam)) +
  geom_jitter() + 
    # geom_violin(alpha = 0.5, draw_quantiles = c(0.5)) +
    ggtitle("Content Trust Scores (K-Means Clustering)") +
  facet_grid(vars(Condition))

```

```{r}


cleaned_data |>
    ggplot(aes(x = Condition, y = anthropomorphism_score)) +
  geom_col() + 
    # geom_violin(alpha = 0.5, draw_quantiles = c(0.5)) +
    ggtitle("Anthropomorphism Scores (K-Means Clustering)") #+
  # facet_grid(vars(Cluster.kmeans))


```

```         
```

```         
```
