---
title: "Power Analysis"
author: "Caroline Simpson"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(pwr)
library(Superpower)

citation()
version$version.string

citation("pwr")
packageVersion("pwr")

citation("Superpower")
packageVersion("Superpower")
```


## Power analysis for Experiment 1

Using 3 levels for the anthropomorphism condition.

Three levels of anthropomorphism (computer, anthropomorphized computer, human)

Small Effect

```{r}
pwr.anova.test(k=3,f=.1,sig.level=.05,power=.8)
```

Medium Effect

```{r}
pwr.anova.test(k=3,f=.3,sig.level=.05,power=.8)
```

Large Effect

```{r}
pwr.anova.test(k=3,f=.5,sig.level=.05,power=.8)
```

Set Number participants

```{r}
pwr.anova.test(k=3, n=80, power=.8)
```

## Power analysis for Experiment 2

Using 2 levels for the anthropomorphism condition.

Three levels of anthropomorphism (computer, anthropomorphized computer, human)

Small Effect

```{r}
pwr.anova.test(k=2,f=.1,sig.level=.05,power=.8)
```

Medium Effect

```{r}
pwr.anova.test(k=2,f=.3,sig.level=.05,power=.8)
```

Large Effect

```{r}
pwr.anova.test(k=2,f=.5,sig.level=.05,power=.8)
```

Set Number participants

```{r}
pwr.anova.test(k=2, n=80, power=.8)
```

```{r}
pwr.anova.test(k=2, n=100, power=.8)
```

