---
title: "scratch"
author: "Caroline Simpson"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(pwr)
library(Superpower)

citation()
version$version.string

citation("pwr")
packageVersion("pwr")

citation("Superpower")
packageVersion("Superpower")
```

## Power analysis for proposal

Using 5 levels for the anthropomorphism condition.

Four levels of anthropomorphism (none, low, high, human) + condition with no vignette

Small Effect

```{r}
pwr.anova.test(k=5,f=.1,sig.level=.05,power=.8)
```

Medium Effect

```{r}
pwr.anova.test(k=5,f=.3,sig.level=.05,power=.8)
```

Large Effect

```{r}
pwr.anova.test(k=5,f=.5,sig.level=.05,power=.8)
```

## Power analysis for proposal

Using 3 levels for the anthropomorphism condition.

Three levels of anthropomorphism (computer, anthropomorphized computer, human)

Small Effect

```{r}
pwr.anova.test(k=3,f=.1,sig.level=.05,power=.8)
```

Medium Effect

```{r}
pwr.anova.test(k=3,f=.3,sig.level=.05,power=.8)
```

Large Effect

```{r}
pwr.anova.test(k=3,f=.5,sig.level=.05,power=.8)
```

Set Number participants

```{r}
pwr.anova.test(k=3, n=80, power=.8)
```

## Power analysis for proposal

Using 2 levels for the anthropomorphism condition.

Three levels of anthropomorphism (computer, anthropomorphized computer, human)

Small Effect

```{r}
pwr.anova.test(k=2,f=.1,sig.level=.05,power=.8)
```

Medium Effect

```{r}
pwr.anova.test(k=2,f=.3,sig.level=.05,power=.8)
```

Large Effect

```{r}
pwr.anova.test(k=2,f=.5,sig.level=.05,power=.8)
```

Set Number participants

```{r}
pwr.anova.test(k=2, n=80, power=.8)
```

```{r}
pwr.anova.test(k=2, n=100, power=.8)
```

```{r}

design = "2b*3b"
n = 100
mu = c(1, 3, 3.5, 3, 4, 4.5)
sd = 1

design_result <- ANOVA_design(design, n, mu, sd,
	labelnames = c("Credulity", "low", "high", "Anthropomorphism", "None", "Some", "Human"))

ANOVA_power(design_result = design_result)
```

Small Effect

```{r}
pwrss.f.ancova(eta2 = 0.01, n.levels = c(2,3),
               alpha = 0.05, power = 0.80)
```

Medium Effect

```{r}
pwrss.f.ancova(eta2 = 0.06, n.levels = c(2,3),
               alpha = 0.05, power = 0.80)
```

Large Effect

```{r}
design2 <- pwrss.f.ancova(eta2 = 0.14, n.levels = c(2,3),
               alpha = 0.05, power = 0.80)

plot(design2)
```
